QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-11-20 Revision/Paper_Rev.tex
Rev_V8.8

%\subsubsection{Time-sensetive approachs}  
For time-sensitive applications, minimizing task delay is the primary optimization objective, driving the development of delay-optimal approaches in MEC. 
To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
Given the dynamic nature of MEC systems, in \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control.

@@

For energy-constrained MEC environments, reducing energy consumption becomes a key objective, motivating the creation of energy-efficient approaches. 
To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
%Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility. 
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently. 
Some research addresed deadline-constraint tasks in energy-constrained MEC and proposed DRL-based approaches to strik a trade-off between task completion/drop ratio and energy consumption.
 To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network. 
Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.

@@

To address time-sensitive applications in energy-constrained MEC systems, striking a trade-off between delay and energy is the primary optimization objective, driving the development of delay-energy-optimal approaches in MEC.
%For example, task offloading must navigate trade-offs between delay and energy consumption, as well as balance energy usage with the number of completed tasks. 
%\subsubsection{Delay-Energy Trade-off approaches} 
Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments. 
 Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
 Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions.

 To address time-sensitive applications with prossecing deadline in energy-constrained MEC systems, achiving a balancing among delay, energy, and number of compeleted task is the optimization objective.
  In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.
 To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm. 
  In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 
   Some reasearch takes deadline-constraint tasks to ensure that the minimized trade-off be within the maximum tolerated delay.
  Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
  Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay.

 \newpage

To address time-sensitive applications with proccessing deadline, Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs.

@@

Specifically, incorporating processing deadlines for time-sensitive applications in energy-constrained MEC systems adds significant complexity to the problem. This requires not only managing task delays and energy consumption but also maximizing the number of successfully completed tasks.
To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.
%%%%To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration.

@@

 Althogh each of delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems, but considering one of them as optimization objective \cite{li2022integrated}--\cite{dai2020edge}, which represents a significant research focus in MEC, can not reflect user satisfaction.

 Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks or processing deadline.

 Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the MDs' individual preferences.
 In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

 Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC. Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results. Additionally, some research has prioritized maximizing the number of completed tasks, highlighting the advantages that MEC systems offer. Therefore, delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems. However, to the best of our knowledge, there has been limited research that simultaneously addresses all three objectives.
 Different from works \cite{li2022integrated}-\cite{dai2020edge}, which only focus on delay-optimal optimization or energy-efficient optimization, we are motivated to emphasize the MEC system with delay, energy consumption, and the number of completed tasks as three objectives for QoE optimization. Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the MDs' individual preferences.
 In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

 In MEC environments, multiple objectives often compete, requiring a balance in decision-making. For instance, task offloading must carefully navigate trade-offs between delay and energy consumption, as well as balance energy usage against the number of completed tasks.

 Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC.

 Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results.

 Research has increasingly addressed these multi-objective optimization challenges.

@@

 				\cite{tang2022double}  & Computation offloading & Minimize total system delay & DDQN & Not consider system energy consumtion \\ \midrule

@@

\subsection{Analysis and Motivation}
Despite extensive research efforts, task offloading continues to encounter significant challenges in real-world scenarios involving multiple MDs and ENs. We discuss these challenges from two aspects, i.e., system modeling and target objective optimization.

  \subsubsection{System modeling}

Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks. In contrast, our research addresses a more realistic MEC scenario, considering delay-sensitive tasks with processing deadlines. This is challenging due to the interplay between processing deadlines, load dynamics at the ENs, and the resulting offloaded task delays. Additionally, the absence of robust underlying resource scheduling systems can lead to data congestion during transmission and inefficient resource allocation, hindering overall system performance \cite{wang2020reinforcement}--\cite{chen2021drl}. Hence, more accurate MEC models are necessary to handle the complexities of dynamic resource scheduling in large-scale scenarios.
To better represent real-world scenarios, authors in \cite{Bolourian-WCL24}--\cite{9253665} have applied queuing theory to model MEC systems. This approach helps capture the dynamic nature of networks, enabling MEC systems to allocate computational and transmission resources more efficiently. In a similar vein, we approached the offloading process as a holistic queuing system, where multiple queues ensure fair resource scheduling for MEC, leading to more accurate and efficient resource management.

@@

 \subsubsection{Optimization Objectives}
Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC. Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results. Additionally, some research has prioritized maximizing the number of completed tasks, highlighting the advantages that MEC systems offer. Therefore, delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems. However, to the best of our knowledge, there has been limited research that simultaneously addresses all three objectives.
Different from works \cite{li2022integrated}-\cite{dai2020edge}, which only focus on delay-optimal optimization or energy-efficient optimization, we are motivated to emphasize the MEC system with delay, energy consumption, and the number of completed tasks as three objectives for QoE optimization. Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the MDs' individual preferences.
In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

@@

\vspace{-5mm}

@@

\vspace{5mm}

@@

\section{Conclusion}\label{section:VII}

%In this study, our focus was directed towards addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. To address this challenge, we propose the QECO algorithm specifically designed to empower MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs but also effectively manages the ever-changing system environment. Through extensive simulations, we demonstrate that QECO outperforms several established benchmark techniques. Specifically, it can significantly increase the average user's QoE. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, according to the user's demands under different system conditions.

%There are multiple directions for extend this research. A complementary approach involves extending the simplified task model by considering dependent divisible tasks that correspond to actual computational tasks. This can be achieved by incorporating a call graph~\cite{kwok1996dynamic} representation to develop relationships among task partitions. Furthermore, in order to accelerate the learning of optimal offloading policies, it is beneficial to enable MDs to take advantage of federated learning~\cite{li2020federated} techniques in the training process. This allows MDs to collectively contribute to improving the offloading model and enables continuous learning when new MDs join the network.

In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QECO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we showed that QECO outperforms several established benchmark techniques, while demonstrating a rapid training convergence. Specifically, QECO increases the average user's QoE by 29.8\%\,--\,37.1\% compared to several existing algorithms. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.

>>>>

%\subsubsection{Time-sensetive approachs}

@@

%Wang et al. in \cite{wang2020reinforcement} studied the computation offloading problem in MEC systems within cellular networks, emphasizing mobile awareness. They proposed a joint approach for task offloading and computation allocation, aiming to address the task offloading costs associated with user mobility.

@@

%For example, task offloading must navigate trade-offs between delay and energy consumption, as well as balance energy usage with the number of completed tasks. 
%\subsubsection{Delay-Energy Trade-off approaches}

%%%To address time-sensitive applications with proccessing deadline, Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs.

@@

%%%Specifically, incorporating processing deadlines for time-sensitive applications in energy-constrained MEC systems adds significant complexity to the problem. This requires not only managing task delays and energy consumption but also maximizing the number of successfully completed tasks.
%%%To further enhance the modeling of real-world scenarios, some studies have applied queuing theory to model MEC systems, which helps capture the dynamic nature of the network and allows MEC systems to allocate computational and transmission resources more efficiently.
%%%%To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network.

%%%%Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration.

@@

For time-sensitive applications, minimizing task delay is the primary optimization objective, driving the development of delay-optimal approaches in MEC. 
To minimize total delay and reduce mobile vehicle task waiting time, Tang \textit{et al.} in \cite{tang2022double} developed a dynamic offloading model for multiple mobile vehicles, segmenting tasks into sequential subtasks for more precise offloading decisions.
Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources. In \cite{li2022integrated} the authors proposed an integrated optimization framework, which leverages past experience and model knowledge to enable fast and resilient real-time offloading control. However, delay-optimal approaches often sacrifice other key performance metrics, such as computation rate and energy consumption, to achieve their goal.

For energy-constrained MEC systems, reducing energy consumption becomes a key objective, motivating the creation of energy-efficient approaches. 
To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. 
Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility.
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm based on deep deterministic policy gradient (DDPG) to optimize resource allocation and computation offloading concurrently. 
To ensure that minimizing energy consumption does not lead to a reduction in the system's computing rate, some researches have expanded their work by incorporating the maximum tolerable delay for task models.
 To address the privacy-aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} modeled the problem as an MDP and proposed a DQN-based method to optimize the computation rate and energy consumption in a queuing-based IIoT network. 
Huang \textit{et al.} in \cite{huang2021deadline} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. 
However, energy-efficient approaches, even when considering deadline constraints, do not adequately address the complexities of time-sensitive applications, particularly in scenarios where reducing delay can have significant effects on the user's QoE.

To address time-sensitive applications in energy-constrained MEC systems, striking a trade-off between delay and energy is the primary optimization objective.
Liao \textit{et al.} in \cite{liao2023online} introduced a double DQN (DDQN)-based algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
To optimize delay and energy consumption, Wu \textit{et al.} in \cite{wu2023multi} investigated the computation offloading problem in a queuing-based MEC IIoT system. They modeled the problem as a POMDP and proposed a multi-agent proximal policy optimization (PPO)-based method to obtain the optimal offloading strategy in dynamic environments. 
 Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the IIoT systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay.
 Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
 Although delay-energy trade-off approaches effectively address time-sensitive tasks, they fail to support tasks with processing deadlines. This is challenging to address, as processing deadlines impact the load dynamics at the ENs, which in turn affect the delay of offloaded tasks.

Incorporating task processing deadlines for time-sensitive applications in energy-constrained MEC systems requires achieving an effective balance among delay, energy consumption, and computation rate. 
  In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.
 To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm. 
  In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 
   Some reasearch takes deadline-constraint tasks to ensure that the minimized trade-off be within the maximum tolerated delay.
  Chen \textit{et al.} in \cite{chen2021drl} addressed a joint optimization problem involving computation offloading and resource allocation, aiming to reduce both task processing delay and energy consumption across all MDs.
  Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. 
Nevertheless, QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements. According to the MDs' individual preferences, each delay, energy consumption, and computation rate may take precedence over two others. While studies \cite{chen2021drl}-\cite{gao2022large} have explored these factors, they overlook user-specific demands and fail to meet QoE requirements effectively.

  Different from aformentioned works []-[], we are motivated to effectively address QoE optimization, where QoE accounts for task completion rate, processing delay, and energy consumption. To effectively address personalized QoE optimization, we designed an adaptive balance for these factors according to the user's preferences, such as prioritizing reduced task delay or energy saving, which may vary over time. Each user may have unique QoE requirements at any given time.

%Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks. In contrast, our research addresses a more realistic MEC scenario, considering delay-sensitive tasks with processing deadlines. This is challenging due to the interplay between processing deadlines, load dynamics at the ENs, and the resulting offloaded task delays. Additionally, the absence of robust underlying resource scheduling systems can lead to data congestion during transmission and inefficient resource allocation, hindering overall system performance \cite{wang2020reinforcement}--\cite{chen2021drl}. Hence, more accurate MEC models are necessary to handle the complexities of dynamic resource scheduling in large-scale scenarios.
%To better represent real-world scenarios, authors in \cite{Bolourian-WCL24}--\cite{9253665} have applied queuing theory to model MEC systems. This approach helps capture the dynamic nature of networks, enabling MEC systems to allocate computational and transmission resources more efficiently. In a similar vein, we approached the offloading process as a holistic queuing system, where multiple queues ensure fair resource scheduling for MEC, leading to more accurate and efficient resource management.

@@

 				\cite{tang2022double}  & Computation offloading & Minimize total system delay & DDQN & Overlooking energy consumtion \\ \midrule

@@

%\subsection{Analysis and Motivation}
%Despite extensive research efforts, task offloading continues to encounter significant challenges in real-world scenarios involving multiple MDs and ENs. We discuss these challenges from two aspects, i.e., system modeling and target objective optimization.

 % \subsubsection{System modeling}

%Some existing works primarily focus on simplified MEC networks, investigating single MEC network models. For instance, studies \cite{zhou2021deep}, \cite{liu2021learn} only examine single-server or single-user scenarios, while \cite{huang2019deep}--\cite{wu2023computation} do not account for delay-sensitive tasks. In contrast, our research addresses a more realistic MEC scenario, considering delay-sensitive tasks with processing deadlines. This is challenging due to the interplay between processing deadlines, load dynamics at the ENs, and the resulting offloaded task delays. Additionally, the absence of robust underlying resource scheduling systems can lead to data congestion during transmission and inefficient resource allocation, hindering overall system performance \cite{wang2020reinforcement}--\cite{chen2021drl}. Hence, more accurate MEC models are necessary to handle the complexities of dynamic resource scheduling in large-scale scenarios.
%To better represent real-world scenarios, authors in \cite{Bolourian-WCL24}--\cite{9253665} have applied queuing theory to model MEC systems. This approach helps capture the dynamic nature of networks, enabling MEC systems to allocate computational and transmission resources more efficiently. In a similar vein, we approached the offloading process as a holistic queuing system, where multiple queues ensure fair resource scheduling for MEC, leading to more accurate and efficient resource management.

%In addition, the limited processing capacities of ENs necessitate careful consideration when allocating resources to MDs. The processing capacity allocated to an MD depends on the dynamic workload of an EN at any given time. Some studies have failed to account for these challenges in dynamic network environments, resulting in reduced system performance. For example, in \cite{chen2021drl}, it is assumed that MDs have sufficient transmission and computation resources from ENs, which may not reflect real-world conditions. While the works \cite{zhao2019deep}, \cite{dai2020edge}, and \cite{wu2024privacy} investigated limited resources in MEC, they did not consider dynamic workloads at ENs in decision-making processes, leading to potential performance issues.
%Certain studies such as \cite{sun2024hierarchical}, \cite{gong2022edge}-\cite{gao2022large} have addressed load levels at ENs and proposed task offloading algorithms. However, these algorithms often require global system information, resulting in high signaling overhead. In contrast to these works, we propose a distributed algorithm that effectively manages unknown load dynamics at ENs. This algorithm enables each MD to make offloading decisions independently, without requiring information (e.g., task models, offloading decisions) from other MDs, thereby reducing signaling overhead and improving overall system performance.

@@

 %\subsubsection{Optimization Objectives}
%Considering delay and energy consumption as optimization objectives represents a significant research focus in MEC. Most existing studies tend to optimize these two objectives independently, often neglecting the conflicts that arise between them, which can lead to skewed optimization results. Additionally, some research has prioritized maximizing the number of completed tasks, highlighting the advantages that MEC systems offer. Therefore, delay, energy consumption, and the number of completed tasks are critical factors in the design of MEC systems. However, to the best of our knowledge, there has been limited research that simultaneously addresses all three objectives.
%Different from works \cite{li2022integrated}-\cite{dai2020edge}, which only focus on delay-optimal optimization or energy-efficient optimization, we are motivated to emphasize the MEC system with delay, energy consumption, and the number of completed tasks as three objectives for QoE optimization. Multi-objective studies \cite{chen2021drl}-\cite{gao2022large} have mostly investigated the trade-off between two or three of these factors but fail to properly address user demands and fulfill QoE requirements. QoE is a time-varying performance measure that reflects user satisfaction, where each user may have unique QoE requirements according to the MDs' individual preferences.
%In contrast to \cite{li2022integrated}-\cite{gao2022large}, to effectively address personalized QoE optimization, we define an adaptive trade-off between task completion and cost reduction. We introduce a weighted sum between completion delay and energy consumption as an associated cost. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes. \color{black}

@@

@@

@@

\section{Conclusion}
\label{section:VII}
%In this study, our focus was directed towards addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. To address this challenge, we propose the QECO algorithm specifically designed to empower MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs but also effectively manages the ever-changing system environment. Through extensive simulations, we demonstrate that QECO outperforms several established benchmark techniques. Specifically, it can significantly increase the average user's QoE. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, according to the user's demands under different system conditions. 
%There are multiple directions for extend this research. A complementary approach involves extending the simplified task model by considering dependent divisible tasks that correspond to actual computational tasks. This can be achieved by incorporating a call graph~\cite{kwok1996dynamic} representation to develop relationships among task partitions. Furthermore, in order to accelerate the learning of optimal offloading policies, it is beneficial to enable MDs to take advantage of federated learning~\cite{li2020federated} techniques in the training process. This allows MDs to collectively contribute to improving the offloading model and enables continuous learning when new MDs join the network.
In this paper, we focused on addressing the challenge of offloading in MEC systems, where strict task processing deadlines and energy constraints adversely impact system performance. We formulated an optimization problem that aims to maximize the QoE of each MD individually, while QoE reflects the energy consumption and task completion delay. To address the dynamic and uncertain mobile environment, we proposed a QoE-oriented DRL-based computation offloading algorithm called QECO. Our proposed algorithm empowers MDs to make offloading decisions without relying on knowledge about task models or other MDs' offloading decisions. The QECO algorithm not only adapts to the uncertain dynamics of load levels at ENs, but also effectively manages the ever-changing system environment. Through extensive simulations, we showed that QECO outperforms several established benchmark techniques, while demonstrating a rapid training convergence. Specifically, QECO increases the average user's QoE by 29.8\%\,--\,37.1\% compared to several existing algorithms. This advantage can lead to improvements in key performance metrics, including task completion rate, task delay, and energy consumption, under different system conditions and varying user demands.
